---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


```{r}
library(rethinking)
library(LaplacesDemon)
library(gtools)
```

```{r}

m2 = 1000

A3 = matrix(0,nrow = m2, ncol = 4)
B3 = A3
C3 = A3
D = A3
D2 = A3
E = A3
F = sample(c(1,4), size = m2, replace = TRUE)
N = sample(c(15,50), m2, replace = TRUE)


for (m in 1:m2) {

n = N[m]
A = matrix(0,nrow = n, ncol = 4)
B = A
C = A

p = runif(4)

for (i in 1:4) {
  A[,i] = sample(1:10, n, replace = TRUE)
  B[,i] = rcat(n, c(4,16,22))
  C[,i] = 10 * rbinom(n, 1, p[i])
}

B = 3 * (B-2)

A2 = A
B2 = B + C

for (i in 2:n) {
  A2[i,] = A2[i-1,] + A[i,]
  B2[i,] = B2[i-1,] + B[i,] + C[i,]
}

A3[m,] = A2[n,]
E[m,] = B2[n,]

for (i in 1:n) {
  for (k in 1:4) {
    t1 = (1+sum(D[m])%%4)*10
    if (A2[i,k] > (D[m,k]+1) * 42 & B2[i,k] > t1) {
      D[m,k] = D[m,k] + 1
      B2[,k] - t1
    }
  }
}

for (i in 1:4) {
  B3[m,i] = sum(B[,i])
  C3[m,i] = sum(C[,i])
  t = 0
  for (j in 1:4) if (D[m,i] > D[m,j] | (D[m,i] == D[m,j] & B2[n,i] >= B2[n,j])) t = t + 1
  if (t == 4) D2[m,i] = 1
}

}

dat2 = matrix(nrow = m2, ncol = 6)

dat3 = data.frame(player = F, turns = as.factor(N))

for (i in 1:m2) {
  dat2[i,] = c(F[i], A3[i,F[i]], E[i,F[i]], D[i,F[i]], N[i], D2[i,F[i]])
  if(F[i]==4) dat2[i,1] = 2
  
  dat3$moves[i] = A3[i,dat3$player[i]]
  dat3$coins[i] = E[i,dat3$player[i]]
  dat3$stars[i] = D[i,dat3$player[i]]
  dat3$win[i] = D2[i,dat3$player[i]]
}

dat3$player = as.factor(dat3$player)

```

***1.***

$(stars | turns = 15) \sim N(\mu,\sigma)$
$\mu = bc*coins + bm*moves$
$bc, bm \sim logN(0,1)$
$\sigma \sim exp(1)$

```{r, include = FALSE}

dat = dat3[dat3$turns==15,]

param = list(
  M = standardize(dat$moves),
  C = standardize(dat$coins),
  S = standardize(dat$stars)
)

model_1.1.1 = ulam(alist(
  S ~ dnorm(mu, sigma),
  mu <- bc*C + bm*M,
  bc ~ dlnorm(0,1),
  bm ~ dlnorm(0,1),
  sigma ~ dexp(1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)
               
```

```{r}
precis(model_1.1.1)
plot(precis(model_1.1.1))
```

$(stars | turns = 15) \sim N(\mu,\sigma)$
$\mu = a*I[player=1] + bc*coins + bm*moves$
$bc, bm \sim logN(0,1)$
$a \sim N(0,1)$
$\sigma \sim exp(1)$

$(stars | turns = 15) \sim N(\mu,\sigma)$
$\mu = bc[player]*coins + bm[player]*moves$
$bc[player], bm[player] \sim logN(0,1)$
$\sigma \sim exp(1)$

$(stars | turns = 15) \sim N(\mu,\sigma)$
$\mu = a*I[player=1] + bc[player]*coins + bm[player]*moves$
$bc[player], bm[player] \sim logN(0,1)$
$a \sim N(0,1)$
$\sigma \sim exp(1)$

```{r, include = FALSE}

param = list(
  P = dat$player,
  M = standardize(dat$moves),
  C = standardize(dat$coins),
  S = standardize(dat$stars)
)

model_1.1.2 = ulam(alist(
  S ~ dnorm(mu, sigma),
  mu <- a*(P-1) + bc*C + bm*M,
  bc ~ dlnorm(0,1),
  bm ~ dlnorm(0,1),
  a ~ dnorm(0,1),
  sigma ~ dexp(1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)
            

model_1.1.3 = ulam(alist(
  S ~ dnorm(mu, sigma),
  mu <- a*(P-1) + bc[P]*C + bm[P]*M,
  bc[P] ~ dlnorm(0,1),
  bm[P] ~ dlnorm(0,1),
  a ~ dnorm(0,1),
  sigma ~ dexp(1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)
               


model_1.1.4 = ulam(alist(
  S ~ dnorm(mu, sigma),
  mu <- bc[P]*C + bm[P]*M,
  bc[P] ~ dlnorm(0,1),
  bm[P] ~ dlnorm(0,1),
  sigma ~ dexp(1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)
               
```

```{r}
compare(model_1.1.1, model_1.1.2, model_1.1.3, model_1.1.4)
```

```{r}
precis(model_1.1.3, depth = 2)
plot(precis(model_1.1.3, depth = 2))
```

```{r}
precis(model_1.1.2, depth = 2)
plot(precis(model_1.1.2, depth = 2))
```

```{r, include = FALSE}
model_1.1.2.2 = ulam(alist(
  S ~ dnorm(mu, sigma),
  mu <- a*(P-1) + bc*C + bm*M,
  bc ~ dlnorm(0,1),
  bm ~ dlnorm(0,1),
  a ~ dlnorm(0,1),
  sigma ~ dexp(1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)
            

model_1.1.3.2 = ulam(alist(
  S ~ dnorm(mu, sigma),
  mu <- a*(P-1) + bc[P]*C + bm[P]*M,
  bc[P] ~ dlnorm(0,1),
  bm[P] ~ dlnorm(0,1),
  a ~ dlnorm(0,1),
  sigma ~ dexp(1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)
```

$a \sim N(0,1)$ -> $a\sim LogN(0,1)$

```{r}
compare(model_1.1.2, model_1.1.3, model_1.1.2.2, model_1.1.3.2)
```

$bc -> bc[player]$, $bm[player] -> bm$

```{r, include = FALSE}

param = list(
  P = dat$player,
  M = standardize(dat$moves),
  C = standardize(dat$coins),
  S = standardize(dat$stars)
)

model_1.1.1.3 = ulam(alist(
  S ~ dnorm(mu, sigma),
  mu <- bc[P]*C + bm*M,
  bc[P] ~ dlnorm(0,1),
  bm ~ dlnorm(0,1),
  sigma ~ dexp(1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)

model_1.1.2.3 = ulam(alist(
  S ~ dnorm(mu, sigma),
  mu <- a*(P-1) + bc[P]*C + bm*M,
  bc[P] ~ dlnorm(0,1),
  bm ~ dlnorm(0,1),
  a ~ dnorm(0,1),
  sigma ~ dexp(1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)
               
```

```{r}
compare(model_1.1.1, model_1.1.2, model_1.1.3, model_1.1.4,model_1.1.1.3, model_1.1.2.3)
```

```{r}
precis(model_1.1.1.3, depth = 2)
plot(precis(model_1.1.1.3, depth = 2))
```

**1.2: 50 turn case**

```{r, include = FALSE}

dat = dat3[dat3$turns==50,]

param = list(
  M = standardize(dat$moves),
  C = standardize(dat$coins),
  S = standardize(dat$stars)
)

model_1.2.1 = ulam(alist(
  S ~ dnorm(mu, sigma),
  mu <- bc*C + bm*M,
  bc ~ dlnorm(0,1),
  bm ~ dlnorm(0,1),
  sigma ~ dexp(1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)

param = list(
  P = dat$player,
  M = standardize(dat$moves),
  C = standardize(dat$coins),
  S = standardize(dat$stars)
)

model_1.2.2 = ulam(alist(
  S ~ dnorm(mu, sigma),
  mu <- a*(P-1) + bc*C + bm*M,
  bc ~ dlnorm(0,1),
  bm ~ dlnorm(0,1),
  a ~ dnorm(0,1),
  sigma ~ dexp(1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)
            

model_1.2.3 = ulam(alist(
  S ~ dnorm(mu, sigma),
  mu <- a*(P-1) + bc[P]*C + bm[P]*M,
  bc[P] ~ dlnorm(0,1),
  bm[P] ~ dlnorm(0,1),
  a ~ dnorm(0,1),
  sigma ~ dexp(1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)

model_1.2.4 = ulam(alist(
  S ~ dnorm(mu, sigma),
  mu <- bc[P]*C + bm[P]*M,
  bc[P] ~ dlnorm(0,1),
  bm[P] ~ dlnorm(0,1),
  sigma ~ dexp(1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)

model_1.2.2.2 = ulam(alist(
  S ~ dnorm(mu, sigma),
  mu <- a*(P-1) + bc*C + bm*M,
  bc ~ dlnorm(0,1),
  bm ~ dlnorm(0,1),
  a ~ dlnorm(0,1),
  sigma ~ dexp(1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)
            

model_1.2.3.2 = ulam(alist(
  S ~ dnorm(mu, sigma),
  mu <- a*(P-1) + bc[P]*C + bm[P]*M,
  bc[P] ~ dlnorm(0,1),
  bm[P] ~ dlnorm(0,1),
  a ~ dlnorm(0,1),
  sigma ~ dexp(1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)

model_1.2.1.3 = ulam(alist(
  S ~ dnorm(mu, sigma),
  mu <- bc[P]*C + bm*M,
  bc[P] ~ dlnorm(0,1),
  bm ~ dlnorm(0,1),
  sigma ~ dexp(1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)

model_1.2.2.3 = ulam(alist(
  S ~ dnorm(mu, sigma),
  mu <- a*(P-1) + bc[P]*C + bm*M,
  bc[P] ~ dlnorm(0,1),
  bm ~ dlnorm(0,1),
  a ~ dnorm(0,1),
  sigma ~ dexp(1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)

```

```{r}
compare(model_1.2.1, model_1.2.2, model_1.2.3, model_1.2.4,model_1.2.1.3, model_1.2.2.3, model_1.2.2.2, model_1.2.3.2)
```

```{r}
precis(model_1.2.1)
plot(precis(model_1.2.1))
```




```{r, include=FALSE, eval = FALSE}

dat = dat2[N==15,]

param = list(
  movement = standardize(dat[,2]),
  coins = standardize(dat[,3]),
  win = dat[,6]
)

model3.2.1 = ulam(alist(
  win ~ dbinom(1, p),
  logit(p) <- A + bc * coins + bm * movement,
  A ~ dnorm(0,1),
  bc ~ dlnorm(0,1),
  bm ~ dlnorm(0,1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)


param = list(
  player = dat[,1],
  movement = standardize(dat[,2]),
  coins = standardize(dat[,3]),
  win = dat[,6]
)

model3.2.2 = ulam(alist(
  win ~ dbinom(1, p),
  logit(p) <- A - bA * (player-1) + bc*coins + bm*movement,
  A ~ dnorm(0,1),
  bA ~ dlnorm(0,1),
  bc ~ dlnorm(0,1),
  bm ~ dlnorm(0,1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)

model3.2.3 = ulam(alist(
  win ~ dbinom(1, p),
  logit(p) <- A - bA * (player-1) + bc[player]*coins + bm[player]*movement,
  A ~ dnorm(0,1),
  bA ~ dlnorm(0,1),
  bc[player] ~ dlnorm(0,1),
  bm[player] ~ dlnorm(0,1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)

model3.2.4 = ulam(alist(
  win ~ dbinom(1, p),
  logit(p) <- A + bc[player]*coins + bm[player]*movement,
  A ~ dnorm(0,1),
  bc[player] ~ dlnorm(0,1),
  bm[player] ~ dlnorm(0,1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)

```

```{r, include=FALSE, eval = FALSE}

compare(model3.2.1, model3.2.2, model3.2.3, model3.2.4)

precis(model3.2.1, depth = 2)
precis(model3.2.2, depth = 2)
precis(model3.2.3, depth = 2)
precis(model3.2.4, depth = 2)

```

```{r, include=FALSE, eval = FALSE}

dat = dat2[N==50,]

param = list(
  movement = standardize(dat[,2]),
  coins = standardize(dat[,3]),
  win = dat[,6]
)

model3.2.1.2 = ulam(alist(
  win ~ dbinom(1, p),
  logit(p) <- A + bc * coins + bm * movement,
  A ~ dnorm(0,1),
  bc ~ dlnorm(0,1),
  bm ~ dlnorm(0,1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)


param = list(
  player = dat[,1],
  movement = standardize(dat[,2]),
  coins = standardize(dat[,3]),
  win = dat[,6]
)

model3.2.2.2 = ulam(alist(
  win ~ dbinom(1, p),
  logit(p) <- A - bA * (player-1) + bc*coins + bm*movement,
  A ~ dnorm(0,1),
  bA ~ dlnorm(0,1),
  bc ~ dlnorm(0,1),
  bm ~ dlnorm(0,1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)

model3.2.3.2 = ulam(alist(
  win ~ dbinom(1, p),
  logit(p) <- A - bA * (player-1) + bc[player]*coins + bm[player]*movement,
  A ~ dnorm(0,1),
  bA ~ dlnorm(0,1),
  bc[player] ~ dlnorm(0,1),
  bm[player] ~ dlnorm(0,1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)

model3.2.4.2 = ulam(alist(
  win ~ dbinom(1, p),
  logit(p) <- A + bc[player]*coins + bm[player]*movement,
  A ~ dnorm(0,1),
  bc[player] ~ dlnorm(0,1),
  bm[player] ~ dlnorm(0,1)
), data = param, chains = 4, cores = detectCores(), log_lik = TRUE)

```

```{r, include=FALSE, eval = FALSE}

compare(model3.2.1.2, model3.2.2.2, model3.2.3.2, model3.2.4.2)

precis(model3.2.1.2, depth = 2)
precis(model3.2.2.2, depth = 2)
precis(model3.2.3.2, depth = 2)
precis(model3.2.4.2, depth = 2)

```

















